R for Clinical Study Reports and Submission

### 2021-10-28 slides/workshop-slides.Rmd
Deploying to gh-pages from @ elong0527/r4csr@f80ebc7f5c0d9a903568bd8f037d75336c7c182c 🚀

```{r}
library(dplyr)
library(tidyr)
library(r2rtf)
```

```{r, eval = FALSE, include = FALSE}
rmarkdown::render("workshop-slides.Rmd")
```

@@

```{r, out.width="80%", echo = FALSE}
knitr::include_graphics("function_summary.PNG")
```

>>>>

```{r, message=FALSE}
library(dplyr)
library(tidyr)
library(r2rtf)
```

@@

```{r, out.width="80%", echo=FALSE, fig.align="center"}
knitr::include_graphics("function-summary.png")
```
